Type Error Telemetry at Scale

### 2023-09-24 programming23/paper.tex
checkpoint: diagram telemetry record, rewrite sec 3

\begin{figure}
  \fbox{
  }
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|}\midrule
    meta & size & te count & fs count & te 0 & te 1 & te 2 \ldots
    \\\midrule
  \end{tabular}
  \caption{Struture of a telemetry record}
  \label{f:tdata}
\end{figure}

@@

In order to avoid swamping our telemetry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    0.5\% of runs of the typechecker (approximately 1 in 200 keystrokes)
      in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains nine kinds of data:
\begin{enumerate}
  \item metadata: a psedonymized session identifier, timestamp and session duration,
  \item mode of the current file: (\mnocheck{}, \mnonstrict{}, or \mstrict{}),
  \item reason for sending: (random selection, or file switch),
  \item size of codebase: number of files, and number of lines of code type checked,
  \item size of edit range
  \item overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
    \FILL{} explain previous/current in detail, explain that this data takes up most of the telemetry record
  \item forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item TooComplexErrors: project-wide count for this one specific error type
\end{enumerate}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges, for example, if the user edits at the beginning and end of the
file.
The main benefit of this strategy is that it ensures constant-size telemetry records.

@@

\paragraph{Internal Limits, Code Too Complex}
%% data = out/ctc-info.txt

>>>>

\begin{figure}[t]\centering
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline
    ID & Time & Mode & Reason & Size Info & Overall Counts & Edit Range Counts
    \\\toprule
  \end{tabular}
  \caption{Structure of a telemetry record. There are 13 overall counts and up to 70 edit range counts in each record.}
  \label{f:tdata}
\end{figure}

@@

In order to avoid swamping our telemetry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    0.5\% of runs of the typechecker (approximately 1 in 200 keystrokes)
      in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains seven kinds of data.
Refer to~\cref{f:tdata} for an illustration:
\begin{enumerate}
  \item
    ID: a psedonynimized identifier for the current session
  \item
    Time: one timestamp from the client and one from the server.
    %% timestamp explanation \cref{s:data-cleaning}
  \item
    Mode: type analysis mode of the current file, which is either \mnocheck{},
    \mnonstrict{}, or \mstrict{}.
%% Reason & Size Info & Overall Counts & Edit Range Counts

  \item reason for sending: (random selection, or file switch),
  \item size of codebase: number of files, and number of lines of code type checked,
  \item size of edit range
  \item overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
    \FILL{} explain previous/current in detail, explain that this data takes up most of the telemetry record
  \item forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item TooComplexErrors: project-wide count for this one specific error type
     \cref{s:code-too-complex}
\end{enumerate}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges, for example, if the user edits at the beginning and end of the
file.
The main benefit of this strategy is that it ensures constant-size telemetry records.

@@

\paragraph{Internal Limits, Code Too Complex}
\label{s:code-too-complex}
%% data = out/ctc-info.txt
